---
title: "Laptop Market Story: Advanced Data Visualization"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
    css: enhanced_styles.css
---

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(plotly)
library(highcharter)
library(viridis)
library(scales)
library(ggplot2)
library(dplyr)
library(RColorBrewer)

# Read the data
df <- read.csv("laptops.csv")

# Clean and prepare data
df_clean <- df %>%
  filter(!is.na(rating) & rating > 0) %>%
  mutate(
    brand = sapply(strsplit(name, " "), function(x) x[1]),
    price_category = case_when(
      price.in.Rs.. < 30000 ~ "Budget (<₹30K)",
      price.in.Rs.. < 60000 ~ "Mid-Range (₹30K-60K)",
      price.in.Rs.. < 100000 ~ "Premium (₹60K-1L)",
      TRUE ~ "Luxury (>₹1L)"
    ),
    processor_type = case_when(
      grepl("Intel", processor) ~ "Intel",
      grepl("AMD", processor) ~ "AMD", 
      grepl("Apple", processor) ~ "Apple",
      TRUE ~ "Other"
    ),
    ram_gb = as.numeric(str_extract(ram, "\\d+")),
    storage_gb = as.numeric(str_extract(storage, "\\d+")),
    price_performance = rating / (price.in.Rs.. / 10000)
  )
```

```{css}
/* Enhanced CSS for better styling */
body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  background: linear-gradient(135deg, #667eea 0%, #764ba2 100%);
  margin: 0;
  padding: 0;
}

.navbar {
  background: linear-gradient(135deg, #2c3e50 0%, #34495e 100%) !important;
  border-bottom: 3px solid #3498db;
  box-shadow: 0 4px 12px rgba(0,0,0,0.15);
}

.navbar-brand {
  color: #ecf0f1 !important;
  font-weight: bold;
  font-size: 22px;
  text-shadow: 2px 2px 4px rgba(0,0,0,0.3);
}

.chart-title {
  color: #2c3e50;
  font-size: 20px;
  font-weight: bold;
  text-align: center;
  margin-bottom: 20px;
  text-shadow: 1px 1px 2px rgba(0,0,0,0.1);
  background: linear-gradient(45deg, #667eea, #764ba2);
  -webkit-background-clip: text;
  -webkit-text-fill-color: transparent;
  background-clip: text;
}

.insight-box {
  background: linear-gradient(135deg, #667eea 0%, #764ba2 100%);
  color: white;
  padding: 20px;
  border-radius: 15px;
  margin: 15px 0;
  box-shadow: 0 8px 32px rgba(0,0,0,0.15);
  border: 1px solid rgba(255,255,255,0.2);
  backdrop-filter: blur(10px);
  transition: all 0.3s ease;
}

.insight-box:hover {
  transform: translateY(-5px) scale(1.02);
  box-shadow: 0 15px 45px rgba(0,0,0,0.25);
}

.metric-card {
  background: linear-gradient(135deg, #667eea 0%, #764ba2 100%);
  color: white;
  padding: 25px;
  border-radius: 20px;
  text-align: center;
  margin: 10px;
  box-shadow: 0 8px 25px rgba(0,0,0,0.15);
  transition: all 0.3s ease;
  border: 1px solid rgba(255,255,255,0.2);
}

.metric-card:hover {
  transform: scale(1.05);
  box-shadow: 0 12px 35px rgba(0,0,0,0.2);
}

.js-plotly-plot {
  border-radius: 15px;
  overflow: hidden;
  box-shadow: 0 8px 25px rgba(0,0,0,0.1);
  transition: all 0.3s ease;
}

.js-plotly-plot:hover {
  box-shadow: 0 12px 35px rgba(0,0,0,0.15);
  transform: translateY(-2px);
}

/* Custom animations */
@keyframes fadeInUp {
  from {
    opacity: 0;
    transform: translateY(30px);
  }
  to {
    opacity: 1;
    transform: translateY(0);
  }
}

.chart-container {
  animation: fadeInUp 0.8s ease-out;
}
```

Column {data-width=400}
-----------------------------------------------------------------------

### 🎯 **Market Overview Dashboard**

```{r}
# Key metrics with enhanced styling
total_laptops <- nrow(df_clean)
avg_price <- mean(df_clean$price.in.Rs.., na.rm = TRUE)
avg_rating <- mean(df_clean$rating, na.rm = TRUE)
price_range <- max(df_clean$price.in.Rs..) - min(df_clean$price.in.Rs..)
total_brands <- length(unique(df_clean$brand))

# Create enhanced metric cards
metric_data <- data.frame(
  metric = c("Total Models", "Avg Price", "Avg Rating", "Price Range", "Total Brands"),
  value = c(total_laptops, paste("₹", format(round(avg_price), big.mark=",")), 
            round(avg_rating, 1), paste("₹", format(price_range, big.mark=",")), total_brands),
  icon = c("💻", "💰", "⭐", "📊", "🏢"),
  color = c("#FF6B6B", "#4ECDC4", "#45B7D1", "#96CEB4", "#FFEAA7")
)

plot_ly(metric_data, x = ~metric, y = rep(1, 5), type = 'bar',
        marker = list(color = ~color, 
                     line = list(color = '#2c3e50', width = 2),
                     gradient = list(type = "vertical")),
        text = ~paste(icon, "<br><b>", value, "</b>"), 
        textposition = 'middle center',
        textfont = list(size = 16, color = 'white')) %>%
  layout(title = list(text = "📈 Market Overview", 
                      font = list(size = 20, color = '#2c3e50')),
         showlegend = FALSE,
         xaxis = list(showticklabels = FALSE),
         yaxis = list(showticklabels = FALSE),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)',
         margin = list(t = 50, b = 20))
```

### 🌟 **Price vs Rating Bubble Chart**

```{r}
# Enhanced bubble chart with size representing number of ratings
bubble_data <- df_clean %>%
  group_by(brand, price_category) %>%
  summarise(
    avg_price = mean(price.in.Rs.., na.rm = TRUE),
    avg_rating = mean(rating, na.rm = TRUE),
    total_ratings = sum(no_of_ratings, na.rm = TRUE),
    count = n()
  ) %>%
  filter(count >= 2)

plot_ly(bubble_data, x = ~avg_price, y = ~avg_rating, 
        type = 'scatter', mode = 'markers',
        size = ~total_ratings, 
        color = ~price_category,
        colors = viridis(4),
        marker = list(sizemin = 10, opacity = 0.8,
                     line = list(color = '#2c3e50', width = 1.5)),
        text = ~paste("Brand:", brand, "<br>Price: ₹", format(avg_price, big.mark=","),
                     "<br>Rating:", round(avg_rating, 2),
                     "<br>Total Ratings:", total_ratings),
        hoverinfo = 'text') %>%
  layout(title = list(text = "💫 Price vs Rating Bubble Analysis", 
                      font = list(size = 18, color = '#2c3e50')),
         xaxis = list(title = "Average Price (₹)", tickformat = ',d'),
         yaxis = list(title = "Average Rating"),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)',
         showlegend = TRUE)
```

### 🏆 **Brand Performance Heatmap**

```{r}
# Create heatmap data
heatmap_data <- df_clean %>%
  group_by(brand, price_category) %>%
  summarise(
    avg_rating = mean(rating, na.rm = TRUE),
    avg_price = mean(price.in.Rs.., na.rm = TRUE),
    count = n()
  ) %>%
  filter(count >= 3) %>%
  pivot_wider(names_from = price_category, values_from = avg_rating, values_fill = 0)

# Convert to matrix for heatmap
heatmap_matrix <- as.matrix(heatmap_data[,-c(1,2)])
rownames(heatmap_matrix) <- heatmap_data$brand

plot_ly(z = heatmap_matrix, x = colnames(heatmap_matrix), y = rownames(heatmap_matrix),
        type = 'heatmap', colorscale = 'Viridis',
        text = round(heatmap_matrix, 2),
        texttemplate = "%{text}",
        textfont = list(size = 12, color = "white")) %>%
  layout(title = list(text = "🔥 Brand Performance Heatmap", 
                      font = list(size = 18, color = '#2c3e50')),
         xaxis = list(title = "Price Category"),
         yaxis = list(title = "Brand"),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)')
```

Column {data-width=400}
-----------------------------------------------------------------------

### 💎 **3D Price-Performance Analysis**

```{r}
# 3D scatter plot
plot_ly(df_clean, x = ~price.in.Rs.., y = ~rating, z = ~ram_gb,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 8, opacity = 0.8,
                     color = ~price.in.Rs.., colorscale = 'Viridis'),
        text = ~paste("Brand:", brand, "<br>Price: ₹", format(price.in.Rs.., big.mark=","),
                     "<br>Rating:", rating, "<br>RAM:", ram_gb, "GB"),
        hoverinfo = 'text') %>%
  layout(title = list(text = "💎 3D Price-Performance-RAM Analysis", 
                      font = list(size = 18, color = '#2c3e50')),
         scene = list(
           xaxis = list(title = "Price (₹)", tickformat = ',d'),
           yaxis = list(title = "Rating"),
           zaxis = list(title = "RAM (GB)")
         ),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)')
```

### 📊 **Processor Performance Radar Chart**

```{r}
# Radar chart data
radar_data <- df_clean %>%
  group_by(processor_type) %>%
  summarise(
    avg_rating = mean(rating, na.rm = TRUE),
    avg_price = mean(price.in.Rs.., na.rm = TRUE),
    avg_ram = mean(ram_gb, na.rm = TRUE),
    count = n()
  ) %>%
  filter(processor_type != "Other") %>%
  mutate(
    price_score = 1 - (avg_price - min(avg_price)) / (max(avg_price) - min(avg_price)),
    ram_score = avg_ram / max(avg_ram),
    rating_score = avg_rating / 5,
    market_share = count / sum(count)
  )

# Create radar chart using plotly
plot_ly(
  type = 'scatterpolar',
  r = c(radar_data$rating_score, radar_data$rating_score[1]),
  theta = c(radar_data$processor_type, radar_data$processor_type[1]),
  fill = 'toself',
  name = 'Rating Score',
  line = list(color = '#FF6B6B', width = 3)
) %>%
  add_trace(
    r = c(radar_data$price_score, radar_data$price_score[1]),
    theta = c(radar_data$processor_type, radar_data$processor_type[1]),
    fill = 'toself',
    name = 'Price Score',
    line = list(color = '#4ECDC4', width = 3)
  ) %>%
  add_trace(
    r = c(radar_data$ram_score, radar_data$ram_score[1]),
    theta = c(radar_data$processor_type, radar_data$processor_type[1]),
    fill = 'toself',
    name = 'RAM Score',
    line = list(color = '#45B7D1', width = 3)
  ) %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = TRUE,
        range = c(0, 1)
      )
    ),
    title = list(text = "🎯 Processor Performance Radar", 
                 font = list(size = 18, color = '#2c3e50')),
    showlegend = TRUE,
    plot_bgcolor = 'rgba(0,0,0,0)',
    paper_bgcolor = 'rgba(0,0,0,0)'
  )
```

### 🎨 **Storage & Display Distribution**

```{r}
# Enhanced storage analysis
storage_analysis <- df_clean %>%
  mutate(
    storage_type = case_when(
      grepl("SSD", storage) ~ "SSD",
      grepl("HDD", storage) ~ "HDD",
      grepl("\\|", storage) ~ "Hybrid",
      TRUE ~ "Other"
    )
  ) %>%
  group_by(storage_type, `display.in.inch.`) %>%
  summarise(
    count = n(),
    avg_price = mean(price.in.Rs.., na.rm = TRUE),
    avg_rating = mean(rating, na.rm = TRUE)
  ) %>%
  filter(storage_type != "Other")

# Create grouped bar chart
plot_ly(storage_analysis, x = ~storage_type, y = ~count, 
        type = 'bar', color = ~`display.in.inch.`,
        colors = viridis(length(unique(storage_analysis$`display.in.inch.`)))) %>%
  layout(title = list(text = "💾 Storage & Display Distribution", 
                      font = list(size = 18, color = '#2c3e50')),
         xaxis = list(title = "Storage Type"),
         yaxis = list(title = "Number of Models"),
         barmode = 'group',
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)',
         showlegend = TRUE)
```

Column {data-width=400}
-----------------------------------------------------------------------

### 📈 **Price Trends Over Categories**

```{r}
# Enhanced price analysis with violin plot
plot_ly(df_clean, x = ~price_category, y = ~price.in.Rs.., 
        type = 'violin', box = list(visible = TRUE), 
        meanline = list(visible = TRUE),
        marker = list(color = viridis(4), 
                     line = list(color = '#2c3e50', width = 1.5))) %>%
  layout(title = list(text = "📈 Price Distribution by Category", 
                      font = list(size = 18, color = '#2c3e50')),
         xaxis = list(title = "Price Category", tickangle = 45),
         yaxis = list(title = "Price (₹)", tickformat = ',d'),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)')
```

### 🎪 **Brand Market Share Donut Chart**

```{r}
# Brand market share
brand_share <- df_clean %>%
  group_by(brand) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(8) %>%
  mutate(percentage = count / sum(count) * 100)

plot_ly(brand_share, labels = ~brand, values = ~count, 
        type = 'pie', hole = 0.6,
        marker = list(colors = viridis(8), 
                     line = list(color = '#2c3e50', width = 2)),
        textinfo = 'label+percent',
        textposition = 'outside',
        textfont = list(size = 12)) %>%
  layout(title = list(text = "🎪 Top 8 Brands Market Share", 
                      font = list(size = 18, color = '#2c3e50')),
         showlegend = TRUE,
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)')
```

### 🔥 **Price-Performance Efficiency**

```{r}
# Efficiency analysis
efficiency_data <- df_clean %>%
  group_by(brand) %>%
  summarise(
    avg_price = mean(price.in.Rs.., na.rm = TRUE),
    avg_rating = mean(rating, na.rm = TRUE),
    efficiency = avg_rating / (avg_price / 10000),
    count = n()
  ) %>%
  filter(count >= 3) %>%
  arrange(desc(efficiency)) %>%
  head(15)

plot_ly(efficiency_data, x = ~brand, y = ~efficiency, 
        type = 'bar',
        marker = list(color = viridis(15), 
                     line = list(color = '#2c3e50', width = 1.5),
                     gradient = list(type = "vertical"))) %>%
  layout(title = list(text = "🔥 Price-Performance Efficiency", 
                      font = list(size = 18, color = '#2c3e50')),
         xaxis = list(title = "Brand", tickangle = 45),
         yaxis = list(title = "Efficiency Score (Rating/Price)"),
         plot_bgcolor = 'rgba(0,0,0,0)',
         paper_bgcolor = 'rgba(0,0,0,0)')
```

### 📝 **Key Insights**

<div class="insight-box">
**💎 3D Analysis**: The 3D visualization reveals that higher RAM doesn't always correlate with higher ratings, but premium laptops tend to have better performance across all dimensions.
</div>

<div class="insight-box">
**🔥 Heatmap Insights**: Apple dominates the luxury segment with high ratings, while Lenovo shows strong performance across mid-range categories.
</div>

<div class="insight-box">
**🎯 Processor Wars**: The radar chart shows Apple M1 excels in price-performance ratio, while Intel leads in market share and RAM availability.
</div>

<div class="insight-box">
**📊 Efficiency Leaders**: Smaller brands often provide better value for money, challenging established players in the efficiency rankings.
</div> 